Plant Modeling for an Autonomous Vehicle

### 2022-04-08 poster.tex
Poster Updates
I added some graphs to the poster under the transfer function modeling section.

\end{itemize} 
\vskip -1cm
%\begin{enumerate}
%    \item Employ state-space representation of 2-DOF helicopter:
%    \begin{align*}
%        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
%    \end{align*}
%    \item Use state feedback law
%    \begin{center}
%        \vskip -1cm
%        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
%    \end{center}
%    \vskip -1cm
%    to minimize the quadratic cost function:
%    \begin{align*}
%        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
%    \end{align*}
%    \item Find the solution $\mathbf{S}$ to the Riccati equation
%    \begin{align*}
%        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
%    \end{align*}    
%    \item Calculate gain, $\mathbf{K}$
%    \begin{center}
%        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
%    \end{center}
%\end{enumerate}

>>>>

\end{itemize} 
\vskip -1cm
\begin{figure}
	\centering
	{\includegraphics[width=0.48\linewidth]{figs/img/byWireSteeringTransferFunctionModel}}
		{\includegraphics[width=0.48\linewidth]{figs/img/manualSteeringTransferFunctionModel}}
	\caption{Steering System Estimated Steering Angle Comparison}
\end{figure}

\begin{figure}
	\centering
	{\includegraphics[width=0.48\linewidth]{figs/img/byWireAccelArxModel}}
	{\includegraphics[width=0.48\linewidth]{figs/img/manualAccelTransferFunctionModel}}
	\caption{Acceleration System Estimated Pedal Position Comparison}
\end{figure}
